---
title: "American Community Survey - Census API"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

This repo provides sample R code for pulling American Community Survey data via the Census API, converting the result to a dataframe, and writing out to a CSV.

In order to interact with the API, you will first need to request a [Census API key here.](https://api.census.gov/data/key_signup.html)

Once you have an API key, edit the "Specify Parameters" section of the *pull_acs.R* script to indicate which dataset, year, variables, and geographies you need to access. You can pull data for multiple variables at a time (up to 50) by entering the table/variable name (e.g., ""B01001_001E" for Total Population) as a comma-separated vector. See ["Working with the Census Data API"](https://www.census.gov/content/dam/Census/library/publications/2020/acs/acs_api_handbook_2020_ch02.pdf) for background on how to interpret variable names. If you're pulling 5-year ACS data, you can look up table/variable codes [here](https://api.census.gov/data/2019/acs/acs5/variables.html). For other datasets, look up the dataset in ["Census API: Datasets in /data and its descendants](https://api.census.gov/data.html) and click on the dataset's associated "variables" link.

```{r, eval=FALSE}
# Specify Parameters ------------------------------------------------------

# As needed, edit the values below to match the dataset, year, variables
# and geography for which you would like to pull data.

api.key <- "[Your API Key]"

url <- "https://api.census.gov/data/"
dataset <- "acs/acs5?"
year <- "2019"
var_list <- c("B01001_001E", "B06011_001E") # Comma-separated vector of ACS variables 
geo <- "state:*" # pull data for each individual state
```

## Resources

**How to use the Census API**

* ["What Users Need to Know"](https://www.census.gov/programs-surveys/acs/guidance/handbooks/api.html)
* ["Working with the Census Data API"](https://www.census.gov/content/dam/Census/library/publications/2020/acs/acs_api_handbook_2020_ch02.pdf)
* [Census Developers Page](https://www.census.gov/data/developers.html)

**Datasets Available via the Census API**

* ["Census API: Datasets in /data and its descendants](https://api.census.gov/data.html)
    + For each listed dataset, the page provides links to geographies, variables, and example API calls (URL)

**List of ACS 5-Year Tables/Variables**

* ["Census Data API: Variables in /data/2019/acs/acs5/variables"](https://api.census.gov/data/2019/acs/acs5/variables.html)
